\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}

\pagestyle{empty}

\begin{document}

\begin{center}
    {\LARGE \textbf{Jade Zhao}}\\
    \vspace{0.25em}
    {\small Bloomington, IN \;|\; Madrid, Spain (Spring 2026)}\\
    \vspace{0.25em}
    {\small
      \href{mailto:jlzhao@iu.edu}{jlzhao@iu.edu}
      \;|\;
      \href{https://linkedin.com/in/jadexzhao}{linkedin.com/in/jadexzhao}
      \;|\;
      \href{https://github.com/jadewowgreen}{github.com/jadewowgreen}
    }
    \vspace{0.25em}
\end{center}

\vspace{0.75em}

\section*{Professional Profile}
I build data-driven tools and systems that help people and communities succeed, with a focus on accessibility, ethical AI, and practical impact. My work combines full-stack development thinking with hands-on research and mentorship, including HIPAA-aligned data systems, accessible web experiences, and user-centered learning tools. I care about how solutions feel in real life: what barriers users face, how teams adopt tools over time, and how outcomes translate into measurable progress.

\section*{How I Think}
\begin{itemize}[leftmargin=*]
    \item ``Never discourage anyone who continually makes progress, no matter how slow.'' --- Plato
    \item ``We are what we repeatedly do. Excellence, then, is not an act but a habit.'' --- Aristotle
    \item ``Don't ever think, no matter how old you are, that you don't need to be coached.'' --- Peyton Manning
    \item ``Leadership isn't one person leading a team. It is a group of leaders working together, up and down the chain of command, to lead.'' --- Jocko Willink
    \item ``A true leader stays exhausted, abhors arrogance, and never looks down on the weakest link.'' --- (adapted principle)
    \item ``Wise are those who keep asking questions when everyone around them thinks they know the answers.'' --- J. Bartell
\end{itemize}

\section*{Guiding Principles}

\subsection*{Lifelong Learning}
I treat learning as an ongoing process that improves both my technical work and my mentoring. In practice, that means iterating based on feedback, documenting decisions clearly, and translating complex topics into actionable next steps for others. Whether I am implementing accessibility changes or designing analysis pipelines, I aim to close the gap between ``understood'' and ``usable.''

\subsection*{Student-Centered Approach}
I design and collaborate around the needs of the people who will actually use the tools. This mindset shows up in how I structure systems (clear flows, accessible interfaces, and reliable data handling) and in how I support teams (timely guidance, shared ownership, and practical training). I believe strong outcomes require an environment where users feel supported, respected, and capable of taking the next step.

\section*{Three Pillars of Success (Tech for Good)}
\begin{itemize}[leftmargin=*]
    \item \textbf{Community Building:} build tools and programs that create belonging and reduce friction for users and teams. For example, I supported first-generation and low-income students by consolidating fragmented campus resources into accessible digital tools, and I helped deliver learning experiences through structured mentorship.
    \item \textbf{Technical Excellence:} deliver solutions that work reliably in real contexts. I have developed HIPAA-compliant database systems, built real-time patient monitoring workflows, and implemented accessibility-focused improvements across websites with measurable impact.
    \item \textbf{Equity and Inclusion:} prioritize accessibility and inclusive outcomes from day one. I conduct accessibility audits (WCAG 2.1 AA/AAA) and translate findings into implementation roadmaps so teams can maintain compliance over time.
\end{itemize}

\section*{Education}
\begin{itemize}[leftmargin=*]
    \item \textbf{Indiana University, Luddy School of Informatics, Computing, and Engineering} --- Bloomington, IN\\
    Bachelor of Science in Informatics, Concentration: Business and Society; Minor: Business (Kelley School of Business)\\
    GPA: 3.70 (Class of 2027)\\
    Hudson \& Holland Scholar (full-ride merit); Luddy Direct Admit; Study Abroad: Universidad Complutense de Madrid (Spring 2026) via Hutton program
 \end{itemize}

\section*{Experience}
\begin{itemize}[leftmargin=*]
    \item \textbf{Undergraduate Research Assistant} --- Proactive Health Informatics Research Group, IU Luddy School \hfill September 2025 -- December 2025\\
    Developed HIPAA-compliant database systems using Python and SQL to process patient data; reduced data entry errors by 30\%.\\
    Built real-time patient monitoring systems with data analytics and anomaly detection; reduced workload by 25--40\%.\\
    Researched ethical AI safeguards including audit trails, bias detection, and human oversight mechanisms.

    \item \textbf{Undergraduate Teaching Assistant} --- IU Office of Student Life, Mentoring Services \& Leadership Development \hfill August 2023 -- December 2025\\
    Consolidated fragmented campus resources into accessible digital tools for first-generation and low-income students.\\
    Automated repetitive information-sharing workflows; freed advisors to focus on high-impact guidance.\\
    Supported students navigating study abroad opportunities and international program applications.

    \item \textbf{AI Client Team Lead} --- Laurie Burns McRobbie ServeIT Clinic, Indiana University \hfill January 2024 -- May 2025\\
    Led cross-functional team of 5 students using Agile to build adaptive learning platforms; increased engagement by 45\%.\\
    Designed accessible AI tutoring systems for English language learners and students with learning disabilities.\\
    Implemented ethical AI safeguards including bias detection, transparent decision-making, and educator oversight.
\end{itemize}

\section*{Key Projects}
\begin{itemize}[leftmargin=*]
    \item \textbf{Indiana Phenology Lab Research} \hfill January 2025 -- May 2025\\
    Analyzed environmental science data using Python and data visualization libraries; improved research efficiency by 40\%.\\
    Designed accessible data presentations using D3.js and Figma; achieved WCAG 2.1 AA compliance standards.

    \item \textbf{Middle Way House Website Redesign} \hfill August 2024 -- December 2024\\
    Led website redesign for a domestic violence nonprofit; increased usability by 65\% and conversions by 28\%.\\
    Conducted accessibility audits on 200+ UI components using WAVE and Axe DevTools; achieved WCAG 2.1 AA/AAA compliance.

    \item \textbf{City of Bloomington Digital Accessibility} \hfill January 2024 -- May 2024\\
    Conducted accessibility audits on 10+ municipal websites using automated and manual testing; identified 150+ compliance issues.\\
    Developed actionable recommendations with implementation roadmaps; elevated sites to WCAG 2.1 AA standards.
\end{itemize}

\section*{Skills}
\begin{itemize}[leftmargin=*]
    \item \textbf{Development:} Python, SQL, HTML, CSS, JavaScript, React, Node.js, PostgreSQL, Git/GitHub, D3.js
    \item \textbf{Data \& Systems:} Real-time systems, HIPAA compliance, data governance, ETL, analytics, database design
    \item \textbf{AI \& Ethics:} Bias detection, ethical AI frameworks, human oversight, transparent systems, LLM orchestration
    \item \textbf{Design \& Accessibility:} WCAG 2.1 AA/AAA, Figma, Adobe Creative Suite, user research, WAVE, Axe DevTools
    \item \textbf{Methods:} Agile/Scrum, cross-functional collaboration, human-centered design, accessibility audits
    \item \textbf{Languages:} English (Native), Mandarin Chinese (Professional), Spanish (Elementary)
\end{itemize}

\section*{Interests}
Film photography; sustainable agriculture; cross-cultural tech adoption; and open-source contributions.

\section*{Closing Note}
I am interested in roles where technology and mentorship combine: building accessible systems, supporting learners and teams, and translating research into practical outcomes. If you value inclusive impact and measurable progress, I would love to connect.

\vspace{0.5em}
\textit{Best regards,}\\
\textbf{Jade Zhao}

\end{document}

