% Jade Zhao — three pillars in my words (numbered). No borrowed document shells.

\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}

\pagestyle{empty}
\setlist[enumerate]{leftmargin=*}

\begin{document}

\input{jade-zhao-header}

\vspace{0.5em}
\noindent\rule{\linewidth}{1pt}
\vspace{0.5em}

\noindent\today

\vspace{0.75em}

\noindent
When I choose projects and how I spend a semester, I sort almost everything into three buckets. They overlap---ServeIT taught me that---but they keep me honest.

\section*{Three pillars}

\begin{enumerate}
    \item \textbf{Community}

    I want tools and rituals that make people feel less alone inside big institutions. That has looked like consolidating fragmented campus resources into something first-gen and low-income students can actually navigate, running Agile with a ServeIT client team, and helping peers with study abroad paperwork I have now lived from both sides.

    \item \textbf{Technical depth}

    I am not interested in slide-deck engineering. I want pipelines and interfaces that survive contact with reality: HIPAA-flavored data work, real-time monitoring, Phenology research with honest charts, and nonprofit or civic sites where we can point to before-and-after metrics.

    \item \textbf{First gen \& access}

    Access is a design constraint, not a PDF from legal at the end. I audit with WAVE and Axe, write roadmaps someone can implement, and treat ethical AI guardrails (educators in the loop, bias checks, audit trails) as part of shipping, not an appendix.
\end{enumerate}

\vspace{1em}
\noindent\textit{Best regards,}\\
\textbf{Jade Zhao}

\end{document}
