% Jade Zhao quotes I actually run decisions through + principles in my own words.

\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\input{jade-zhao-pink-highlight}
\usepackage{hyperref}
\usepackage{enumitem}

\pagestyle{empty}
\setlist[itemize]{leftmargin=*}

\newcommand{\sectionboxed}[1]{%
  \vspace{0.75em}%
  \begin{center}%
  \fbox{\parbox{0.92\linewidth}{\centering\bfseries\large #1}}%
  \end{center}%
  \vspace{0.5em}%
}

\begin{document}

\input{jade-zhao-header}
\vspace{0.25em}\newline\noindent\textbf{Notable/bueno (NT) \;|\; Sobresaliente/excelente (SB) \;|\; EU business casual}\n

\vspace{0.5em}
\noindent\rule{\linewidth}{1pt}

\vspace{0.5em}
\noindent\textit{Little reminders I return to when Slack is loud or a spec forgets a person. Not borrowed fluff, just what steadies me.}

\sectionboxed{How I think}

\begin{itemize}
    \item ``Never discourage anyone who continually makes progress, no matter how slow.'' \textit{(Plato)}
    \item ``We are what we repeatedly do. Excellence, then, is not an act but a habit.'' \textit{(Aristotle)}
    \item ``Don't ever think, no matter how old you are, that you don't need to be coached.'' \textit{(Peyton Manning)}
    \item ``Leadership isn't one person leading a team. It is a group of leaders working together, up and down the chain of command, to lead.'' \textit{(Jocko Willink)}
    \item ``A true leader stays exhausted, abhors arrogance, and never looks down on the weakest link.'' \textit{(how I try to lead on teams)}
    \item ``Wise are those who keep asking questions when everyone around them thinks they know the answers.'' \textit{(J. Bartell)}
\end{itemize}

\sectionboxed{What I hold myself to}

\subsection*{Keep learning in public}
Feedback is not a threat to ego; it is fuel. I write things down so the next person is not blocked by my memory. Whether it is WCAG notes or a data pipeline handoff, I want ``understood in the meeting'' to become ``someone can run it Monday.''

\subsection*{Build for who is actually in the room}
First-gen friends decoding a portal, someone on a city website at midnight, a clinician behind a screen I helped wire. They all deserve patience and clarity, not vibes-only empathy.

\subsection*{Product-shaped habits}
Name stakeholders before features. Treat access and ethics as requirements, not a late QA scramble. Prefer small shippable slices with documented assumptions so someone else can trace decisions later.

\subsection*{Say when AI and agents helped}
I use Cursor and agentic assistants; I still read diffs and own what ships. Full transparency (definitions, market-context analogy, SWOT risk register, vendor map, runbook) lives at \href{https://matchaxmoxie.github.io/matchaxmoxie/\#how-i-work}{matchaxmoxie.github.io\#how-i-work}.

\vspace{1em}
\noindent\textit{Best regards,}\\
\textbf{Jade Zhao}

\end{document}
