% Jade Zhao — full narrative profile + résumé body. Original voice; no third-party layout scans.

\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}

\pagestyle{empty}

\begin{document}

\begin{center}
    {\LARGE \textbf{Jade Zhao}}\\
    \vspace{0.25em}
    {\small Bloomington, IN \;|\; Madrid, Spain (Spring 2026)}\\
    \vspace{0.25em}
    {\small
      \href{mailto:jlzhao@iu.edu}{jlzhao@iu.edu}
      \;|\;
      \href{https://linkedin.com/in/jadexzhao}{linkedin.com/in/jadexzhao}
      \;|\;
      \href{https://github.com/jadewowgreen}{github.com/jadewowgreen}
      \;|\;
      \href{https://www.instagram.com/matchaxmoxie/}{@matchaxmoxie}
    }
    \vspace{0.25em}
\end{center}

\vspace{0.75em}

\section*{Who I am}
Chinese American, raised in the US, spending Spring 2026 at Universidad Complutense de Madrid through the Hutton program. I am the same person in a lecture hall and on a real team: direct, prepared, and impatient with tools that only work for the default user. I study informatics with a Business \& Society concentration and a Kelley minor because I want both the implementation detail and the language of risk, stakeholders, and what ``done'' actually means.

\section*{Matchaxmoxie}
\texttt{matchaxmoxie} is my public slice of the internet: pink static HTML, film photos, matcha, plants, Madrid semester energy. It is not a separate persona from the engineer who files clear Slack updates and turns in problem sets on time---it is the reminder that ambition without rest and aesthetics burns out. The site ships with zero frameworks on purpose; I like owning every line that faces the world.

\section*{Professional profile}
I build data-driven tools and systems that help people and communities succeed, with accessibility and ethical AI in the first spec, not the last audit. Work spans HIPAA-aligned health informatics research, ServeIT client delivery, nonprofit and municipal accessibility, and mentoring that turns fragmented campus resources into something first-gen and low-income students can actually use. I care how solutions feel in real life: barriers, adoption over time, and outcomes you can measure.

\section*{How I think}
These lines are not decoration---they are the spine I use when a sprint gets noisy or a requirement forgets the user.

\begin{itemize}[leftmargin=*]
    \item ``Never discourage anyone who continually makes progress, no matter how slow.'' --- Plato
    \item ``We are what we repeatedly do. Excellence, then, is not an act but a habit.'' --- Aristotle
    \item ``Don't ever think, no matter how old you are, that you don't need to be coached.'' --- Peyton Manning
    \item ``Leadership isn't one person leading a team. It is a group of leaders working together, up and down the chain of command, to lead.'' --- Jocko Willink
    \item ``A true leader stays exhausted, abhors arrogance, and never looks down on the weakest link.'' --- (principle I keep in mind)
    \item ``Wise are those who keep asking questions when everyone around them thinks they know the answers.'' --- J. Bartell
\end{itemize}

\section*{Guiding principles}

\subsection*{Keep learning in public}
Iteration, honest documentation, and turning complexity into a next step someone else can take---that is how I mentor and how I build. Whether it is WCAG remediation or a Phenology pipeline, I want the gap between ``we talked about it'' and ``someone can run it'' to close.

\subsection*{Design around real users}
Flows, accessible interfaces, and reliable data handling are not polish; they are the product. So is how I show up for teams: on time, specific, and willing to revise when feedback says I missed something.

\section*{Three pillars (how I choose work)}

\begin{itemize}[leftmargin=*]
    \item \textbf{Community:} Tools and programs that reduce friction and build belonging---especially consolidating campus resources for first-gen and low-income students, ServeIT clients, and people navigating study abroad from both sides of the desk.
    \item \textbf{Technical depth:} HIPAA-aware pipelines, real-time monitoring, Phenology + D3, full-stack shipping---work where the numbers (errors, workload, engagement) tell the truth.
    \item \textbf{First gen \& access:} First-generation and low-income student needs alongside WCAG 2.1 AA/AAA practice---audits, roadmaps, and fixes that stay maintained instead of living in a PDF.
\end{itemize}

\section*{Education}
\begin{itemize}[leftmargin=*]
    \item \textbf{Indiana University, Luddy School of Informatics, Computing, and Engineering} Bloomington, IN\\
    Bachelor of Science in Informatics, Concentration: Business and Society; Minor: Business (Kelley School of Business)\\
    GPA: 3.70 (Class of 2027)\\
    Hudson \& Holland Scholar (full-ride merit); Luddy Direct Admit; Study Abroad: Universidad Complutense de Madrid (Spring 2026) via Hutton program
 \end{itemize}

\section*{Experience}
\begin{itemize}[leftmargin=*]
    \item \textbf{Undergraduate Research Assistant} Proactive Health Informatics Research Group, IU Luddy School \hfill September 2025 -- December 2025\\
    Developed HIPAA-compliant database systems using Python and SQL to process patient data; reduced data entry errors by 30\%.\\
    Built real-time patient monitoring systems with data analytics and anomaly detection; reduced workload by 25--40\%.\\
    Researched ethical AI safeguards including audit trails, bias detection, and human oversight mechanisms.

    \item \textbf{Undergraduate Teaching Assistant} IU Office of Student Life, Mentoring Services \& Leadership Development \hfill August 2023 -- December 2025\\
    Consolidated fragmented campus resources into accessible digital tools for first-generation and low-income students.\\
    Automated repetitive information-sharing workflows; freed advisors to focus on high-impact guidance.\\
    Supported students navigating study abroad opportunities and international program applications.

    \item \textbf{AI Client Team Lead} Laurie Burns McRobbie ServeIT Clinic, Indiana University \hfill January 2024 -- May 2025\\
    Led cross-functional team of 5 students using Agile to build adaptive learning platforms; increased engagement by 45\%.\\
    Designed accessible AI tutoring systems for English language learners and students with learning disabilities.\\
    Implemented ethical AI safeguards including bias detection, transparent decision-making, and educator oversight.
\end{itemize}

\section*{Key projects}
\begin{itemize}[leftmargin=*]
    \item \textbf{Indiana Phenology Lab Research} \hfill January 2025 -- May 2025\\
    Analyzed environmental science data using Python and data visualization libraries; improved research efficiency by 40\%.\\
    Designed accessible data presentations using D3.js and Figma; achieved WCAG 2.1 AA compliance standards.

    \item \textbf{Middle Way House Website Redesign} \hfill August 2024 -- December 2024\\
    Led website redesign for a domestic violence nonprofit; increased usability by 65\% and conversions by 28\%.\\
    Conducted accessibility audits on 200+ UI components using WAVE and Axe DevTools; achieved WCAG 2.1 AA/AAA compliance.

    \item \textbf{City of Bloomington Digital Accessibility} \hfill January 2024 -- May 2024\\
    Conducted accessibility audits on 10+ municipal websites using automated and manual testing; identified 150+ compliance issues.\\
    Developed actionable recommendations with implementation roadmaps; elevated sites to WCAG 2.1 AA standards.
\end{itemize}

\section*{Skills}
\begin{itemize}[leftmargin=*]
    \item \textbf{Development:} Python, SQL, HTML, CSS, JavaScript, React, Node.js, PostgreSQL, Git/GitHub, D3.js
    \item \textbf{Data \& Systems:} Real-time systems, HIPAA compliance, data governance, ETL, analytics, database design
    \item \textbf{AI \& Ethics:} Bias detection, ethical AI frameworks, human oversight, transparent systems, LLM orchestration
    \item \textbf{Design \& Accessibility:} WCAG 2.1 AA/AAA, Figma, Adobe Creative Suite, user research, WAVE, Axe DevTools
    \item \textbf{Methods:} Agile/Scrum, cross-functional collaboration, human-centered design, accessibility audits
    \item \textbf{Languages:} English (Native), Mandarin Chinese (Professional), Spanish (Elementary)
\end{itemize}

\section*{Interests}
Film photography; sustainable agriculture; cross-cultural tech adoption; open-source contributions.

\section*{Closing}
I want roles where technology and mentorship meet: accessible systems, learners and teams who get honest answers, and research that turns into something shippable. If you value first-gen access, measured outcomes, and people who mean what they put on the page, I would love to connect.

\vspace{0.5em}
\textit{Best regards,}\\
\textbf{Jade Zhao}

\end{document}
