% Jade Zhao how I think about mentorship, clients, and shipping usable systems.

\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\input{../shared/jade-zhao-pink-highlight}
\usepackage{hyperref}
\usepackage{parskip}

\pagestyle{empty}
\hypersetup{colorlinks=true,urlcolor=blue}

\begin{document}

\input{../shared/jade-zhao-header}
\vspace{0.35em}
\noindent\textit{April 2026 update: mentorship and delivery philosophy in one-page format (Greco-Latin + English style).}

\vspace{0.5em}
\noindent\rule{\linewidth}{1pt}
\vspace{0.75em}

\noindent\today

\vspace{0.75em}

I try to treat student-facing and client-facing tech with the same discipline I want in teams: gentle pace, clear signals, explicit next steps. Respect time, tell the truth about what we can ship, and leave people with an action they can complete. Mentoring chats, ServeIT sprints, health informatics wiring\ldots\ one question: would I trust this tomorrow morning if I were them?

I care about educational and civic contexts where software reduces administrative drag instead of adding it. That has meant consolidating campus resources into accessible tools, automating repetitive advisor communication, and helping students navigate international applications with better structure than a PDF graveyard.

Good relationships go both ways. I bring documentation, follow-through, and honest estimates; students and stakeholders bring goals and pushback that should change the roadmap. I translate jargon into something you can act on so ``I understood the meeting'' actually becomes ``I know what to do on Monday.''

In research and product-shaped projects I default to agency: interfaces and data flows where humans can correct mistakes, and AI features paired with bias checks, audit trails, and educator oversight so ``innovation'' does not mean ``no one is accountable.''

For how I use AI and agentic coding tools in my own workflow (plain-language definitions, a personal SWOT as a living risk register, vendor map, operating principles, backlog---same vocabulary I use for product and strategy coursework), see \href{https://matchaxmoxie.github.io/matchaxmoxie/\#how-i-work}{matchaxmoxie.github.io\#how-i-work}.

Health informatics, nonprofit redesigns, and clinic work have all forced me to align engineers, domain experts, and end users under shared definitions of risk. There is no solo hero version of that job I believe in.

Accessibility and first-gen student support belong in the same backlog as every other feature. Audits, WCAG fixes, and roadmaps are how I make access real instead of rhetorical.

\vspace{1.5em}
\noindent\textit{Best regards,}\\
\textbf{Jade Zhao}

\end{document}
