% Jade Zhao full narrative profile + résumé body. Original voice; no third-party layout scans.

\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\input{../shared/jade-zhao-pink-highlight}
\usepackage{hyperref}
\usepackage{enumitem}

\pagestyle{empty}

\begin{document}

\begin{center}
    {\LARGE \textbf{Jade Zhao}}\\
    \vspace{0.25em}
    {\small Bloomington, IN \;|\; Madrid, Spain (Spring 2026)}\\
    \vspace{0.25em}
    {\small
      \href{mailto:jadexzhao@outlook.com}{jadexzhao@outlook.com}
      \;|\;
      \href{https://linkedin.com/in/jadexzhao}{linkedin.com/in/jadexzhao}
      \;|\;
      \href{https://github.com/jazhao-ucm}{github.com/jazhao-ucm}
      \;|\;
      \href{https://www.instagram.com/j.adezhao/}{@j.adezhao}
    }
    \vspace{0.25em}
\end{center}

\noindent\textit{April 2026 update: refreshed narrative profile aligned with the latest matchaxmoxie site and documentation style.}

\vspace{0.75em}

\section*{Persona (Who I am)}
Chinese American, raised in the US, Spring 2026 at Universidad Complutense de Madrid through Hutton. I am trying to be the same person in lecture and on a team: kind, prepared, honest when I do not know something, and allergic to tools that quietly assume a ``default'' user who never existed. Informatics (Business \& Society) plus a Kelley minor means I can read a spreadsheet and still ask who gets left out.

{\bfseries Notable/bueno (NT) · Sobresaliente/excelente (SB) · EU business casual}

\section*{Domus Digitalis (Matchaxmoxie)}
\texttt{matchaxmoxie} is my pink corner of the internet: handmade static HTML on the site; \href{https://www.instagram.com/j.adezhao/}{@j.adezhao} on Instagram is mostly what I eat. Film, matcha, plants, Madrid semester brain live around that. It is not a separate brand from the student who does the reading; it is permission to be soft in public. No frameworks on the site on purpose: I like knowing every line that says hello to someone.

\noindent The same site hosts a long, plain-language disclosure of how I use \textbf{Cursor} (editor with repo context and \texttt{.cursorrules}) and \textbf{supervised agents} (multi-step tool use with human diff review), framed as a \textbf{product and governance memo} with a \textbf{business--technology--law} lens: vendor and data-handling awareness, institutional policy, HIPAA- and WCAG-adjacent norms, EU digital rulemaking as scan input---\textbf{risk-aware disclosure} in the vocabulary of strategy and compliance-adjacent coursework. \textbf{Cursor vs.\ agents:} \href{https://matchaxmoxie.github.io/matchaxmoxie/\#cursor-and-agents}{\#cursor-and-agents}; \textbf{triangulation:} \href{https://matchaxmoxie.github.io/matchaxmoxie/\#business-tech-law}{\#business-tech-law}; full memo: \href{https://matchaxmoxie.github.io/matchaxmoxie/\#how-i-work}{\#how-i-work}.

\section*{Strategia (Product and strategy lens)}
Coursework in business, strategy, product management, and EU-focused policy reinforced habits I already used in clinic and civic work: name \textbf{stakeholders} early, treat ethics and access as \textbf{non-functional requirements}, read \textbf{vendor and institutional constraints} alongside user stories, document assumptions for \textbf{traceability}, and ship in \textbf{small increments} with human sign-off when stakes are high. Environmental scan (PEST + legal/regulatory) and SWOT-style thinking are honest labels for ``what could break this roadmap or create liability?''

\section*{Theoria (Professional profile)}
I build data-heavy, human-sized tools: accessibility and ethical AI early, not as a panic pass before launch. Lately that looks like HIPAA-aware health informatics research, ServeIT clients, nonprofit and city websites, and mentoring work that turns a pile of links into something first-gen and low-income students can actually use. I care how a flow feels at 11 p.m., not only in a demo.

\section*{Logos (How I think)}
Quotes I steal when my brain gets loud, same energy as a patient dog sitting next to you until the thing makes sense.

\begin{itemize}[leftmargin=*]
    \item ``Never discourage anyone who continually makes progress, no matter how slow.'' \textit{(Plato)}
    \item ``We are what we repeatedly do. Excellence, then, is not an act but a habit.'' \textit{(Aristotle)}
    \item ``Don't ever think, no matter how old you are, that you don't need to be coached.'' \textit{(Peyton Manning)}
    \item ``Leadership isn't one person leading a team. It is a group of leaders working together, up and down the chain of command, to lead.'' \textit{(Jocko Willink)}
    \item ``A true leader stays exhausted, abhors arrogance, and never looks down on the weakest link.'' \textit{(principle I keep in mind)}
    \item ``Wise are those who keep asking questions when everyone around them thinks they know the answers.'' \textit{(J. Bartell)}
\end{itemize}

\section*{Principia (Guiding principles)}

\subsection*{Keep learning in public}
Write things down, admit when a diagram was wrong, turn a meeting into a checklist someone else can run. That is mentorship and engineering to me: less performance, more handoffs that do not suck.

\subsection*{Design around real people}
Interfaces and data that do not embarrass us later, and teammates who get replies instead of silence. I would rather redo a screen than ship something that only works for me.

\section*{Tria Columnae (Three soft anchors)}

\begin{itemize}[leftmargin=*]
    \item \textbf{People \& warmth:} Fewer sharp edges for first-gen and low-income friends on campus, kind ServeIT collaborations, study-abroad empathy because I have been the confused person with the form.
    \item \textbf{Building \& fixing:} HIPAA-flavored pipelines, monitoring that helps real shifts, Phenology charts, small full-stack things that survive contact with reality.
    \item \textbf{Access \& care:} WCAG habits, audits that become tickets, AI pieces where teachers stay in the loop. If it is only easy for some, we are not finished.
\end{itemize}

\section*{Academia (Education)}
\begin{itemize}[leftmargin=*]
    \item \textbf{Indiana University, Luddy School of Informatics, Computing, and Engineering} Bloomington, IN\\
    Bachelor of Science in Informatics, Concentration: Business and Society; Minor: Business (Kelley School of Business)\\
    GPA: 3.70 (Class of 2027)\\
    Hudson \& Holland Scholar (full-ride merit); Luddy Direct Admit; Study Abroad: Universidad Complutense de Madrid (Spring 2026) via Hutton program
 \end{itemize}

\section*{Experientia (Experience)}
\begin{itemize}[leftmargin=*]
    \item \textbf{Undergraduate Research Assistant}, Proactive Health Informatics Research Group, IU Luddy School \hfill September 2025 to December 2025\\
    Developed HIPAA-compliant database systems using Python and SQL to process patient data; reduced data entry errors by 30\%.\\
    Built real-time patient monitoring systems with data analytics and anomaly detection; reduced workload by 25 to 40\%.\\
    Researched ethical AI safeguards including audit trails, bias detection, and human oversight mechanisms.

    \item \textbf{Undergraduate Teaching Assistant}, IU Office of Student Life, Mentoring Services \& Leadership Development \hfill August 2023 to December 2025\\
    Consolidated fragmented campus resources into accessible digital tools for first-generation and low-income students.\\
    Automated repetitive information-sharing workflows; freed advisors to focus on high-impact guidance.\\
    Supported students navigating study abroad opportunities and international program applications.

    \item \textbf{AI Client Team Lead}, Laurie Burns McRobbie ServeIT Clinic, Indiana University \hfill January 2024 to May 2025\\
    Led cross-functional team of 5 students using Agile to build adaptive learning platforms; increased engagement by 45\%.\\
    Designed accessible AI tutoring systems for English language learners and students with learning disabilities.\\
    Implemented ethical AI safeguards including bias detection, transparent decision-making, and educator oversight.
\end{itemize}

\section*{Projecta (Key projects)}
\begin{itemize}[leftmargin=*]
    \item \textbf{Indiana Phenology Lab Research} \hfill January 2025 to May 2025\\
    Analyzed environmental science data using Python and data visualization libraries; improved research efficiency by 40\%.\\
    Designed accessible data presentations using D3.js and Figma; achieved WCAG 2.1 AA compliance standards.

    \item \textbf{Middle Way House Website Redesign} \hfill August 2024 to December 2024\\
    Led website redesign for a domestic violence nonprofit; increased usability by 65\% and conversions by 28\%.\\
    Conducted accessibility audits on 200+ UI components using WAVE and Axe DevTools; achieved WCAG 2.1 AA/AAA compliance.

    \item \textbf{City of Bloomington Digital Accessibility} \hfill January 2024 to May 2024\\
    Conducted accessibility audits on 10+ municipal websites using automated and manual testing; identified 150+ compliance issues.\\
    Developed actionable recommendations with implementation roadmaps; elevated sites to WCAG 2.1 AA standards.
\end{itemize}

\section*{Instrumenta (Skills)}
\begin{itemize}[leftmargin=*]
    \item \textbf{Development:} Python, SQL, HTML, CSS, JavaScript, React, Node.js, PostgreSQL, Git/GitHub, D3.js
    \item \textbf{Data \& Systems:} Real-time systems, HIPAA compliance, data governance, ETL, analytics, database design
    \item \textbf{AI \& Ethics:} Bias detection, ethical AI frameworks, human oversight, transparent systems, LLM orchestration
    \item \textbf{Design \& Accessibility:} WCAG 2.1 AA/AAA, Figma, Adobe Creative Suite, user research, WAVE, Axe DevTools
    \item \textbf{Methods:} Agile/Scrum, cross-functional collaboration, human-centered design, accessibility audits, lightweight discovery notes and stakeholder alignment
    \item \textbf{Languages:} English (Native), Mandarin Chinese (Professional), Spanish (Elementary)
\end{itemize}

\section*{Studia (Interests)}
Film photography; sustainable agriculture; cross-cultural tech adoption; open-source contributions.

\section*{Conclusio (Closing)}
I want work where tech and mentorship overlap, where access is not a buzzword and research turns into something a person can actually click. If you like gentle humans who still ship, say hi.

\vspace{0.5em}
\textit{Best regards,}\\
\textbf{Jade Zhao}

\end{document}
